### 2018-12-01 Sections/economics_of_the_quantum_internet.tex
Economics update. Roadmap update.

\begin{postulate}[Rate of return]\label{post:RoR}\index{Rate of return}
The RoR is defined as,
\begin{align}
e^{\gamma_\mathrm{ror}} = \frac{n_\mathrm{return}}{n_\mathrm{cost}},
\end{align}
where $n_\mathrm{return}$ is the profit made by licensing out the network's joint compute-power for a single unit of time, given a present-day network value of $n_\mathrm{cost}$.
\end{postulate}

@@

In an ideal market, where hardware cost is completely predictable, e.g perfectly follows the hardware cost model (Pos.~\ref{post:hardware_cost}), the risk asymptotes to zero and perfect arbitrage (Pos.~\ref{post:market_eff}) will drive the RoR to asymptote to the risk-free RoR, \mbox{$\gamma_\mathrm{ror} \to r_\mathrm{rf}$}. Of course, real markets necessarily exhibit risks and uncertainties, and the RoR on quantum hardware will never be truly risk-free, meaning that upon trading off risk for return, we will always observe \mbox{$\gamma_\mathrm{ror} > r_\mathrm{rf}$}.

>>>>

\begin{postulate}[Rate of return]\label{post:RoR}\index{Rate of return}
The RoR is defined as,
\begin{align}
e^{\gamma_\mathrm{ror}(t)} = \frac{R(t)}{V(t)},
\end{align}
where $R(t)$ is the profit made by licensing out the network's joint compute-power for a single unit of time, given a present-day network value of $V(t)$.
\end{postulate}

@@

%
% Market Competitiveness
%

\section{Market competitiveness}\index{Market competitiveness}\index{Efficiency}

\dropcap{R}{ecall} the risk-free RoR is $r_\mathrm{rf}$\index{Risk-free rate of return}. The difference between the RoR on our investment into qubit assets and the risk-free rate effectively tells us our profitability relative to a baseline zero-risk asset. This difference in turn can be interpreted as an indicator of the competitiveness or efficiency of the market -- more efficient and competitive markets exhibit narrower profit windows. This is yields the figure of merit,

\begin{postulate}[Market competitiveness]\label{post:market_comp}\index{Market competitiveness}
The \textit{competitiveness} or \textit{efficiency} of the qubit market is given by the difference between the risk-free RoR and that of our physical qubits,
\begin{align}
\xi_\mathrm{comp} = \gamma_\mathrm{ror} - r_\mathrm{rf}.
\end{align}

There are three distinct regimes for market competitiveness:
\begin{itemize}
	\item \mbox{$\xi_\mathrm{comp}=0$}: The market exhibits perfect efficiency, since price competition\index{Price competition} is so strong that profit windows have narrowed to vanishing point. There is no profit incentive to buy into or sell qubits, since they have converged with the risk-free asset.
	\item \mbox{$\xi_\mathrm{comp}>0$}: The market is profit-making for qubit owners. There is a profit incentive to buy ownership of physical qubits and license them out on the time-share market.
	\item \mbox{$\xi_\mathrm{comp}<0$}: The market is loss-making for qubit owners. Purchasing of physical qubits is disincentivised, since it's more optimal to buy into the zero-risk asset than hold qubit assets.
\end{itemize}
\end{postulate}

The \mbox{$\xi_\textrm{comp}=0$} limit is really a fairly hypothetical regime which ought not to arise in real markets, which necessarily exhibit inefficiencies. However, highly-competitive real markets will asymptote to the efficient regime, \mbox{$\xi_\textrm{comp}\approx 0$}.

### 2018-12-01 Sections/roadmap.tex
Economics update. Roadmap update.

\dropcap{W}{e} have in this work presented a vast number of ideas, protocols, applications and implications for future quantum technology, mediated by the quantum internet. The relationship between all these concepts is highly complex, with a large number of interdependencies. In Fig.~\ref{fig:roadmap} we summarise this via a mind-map\index{Mind-map}, capturing these relationships to show the logical flow of developments that will need to take place to reach various technological destinations.

\begin{figure*}
	\includegraphics[width=\textwidth]{roadmap}
	\caption{Relationships and dependencies in the development and deployment of the major concepts in the quantum internet.}\label{fig:roadmap}
\end{figure*}

>>>>

\dropcap{W}{e} have in this work presented a vast number of ideas, protocols, applications and implications for future quantum technology, mediated by the quantum internet. The relationship between all these concepts is highly complex, with a large number of interdependencies. In Fig.~\ref{fig:roadmap} we express this as a mind-map timeline\index{Mind-map}\index{Timeline}, capturing these relationships to show the logical flow of developments that will need to take place to reach various technological milestones and destinations.

\begin{figure*}
	\includegraphics[clip=true, angle=-90, width=\textwidth]{roadmap}
	\caption{Relationships and dependencies in the development and deployment of the major concepts in the quantum internet, showing the logical flow of developments that will need to take place to reach various technological milestones and destinations.}\label{fig:roadmap}
\end{figure*}
